\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-22 coqimpl.tex

% Concrete details of compilation of a family term data structure
Taking \cref{fig:plugin-example1} as an example: when the user interactively inputs the line "Field a : nat := ..", our plugin will translate this statement into the "Module a_9", "Module Type a_10, a_11" three components. {The "EmptySig" is just empty module type.} Then, these modules and module types will be generated and type-checked by Coq immediately. The computed "Module a_10" is then part of the context of "Field b" (as the module type of "self__A") for "b" to refer to. The internal representation of family "A" is simply the list of these ``compiled'' modules and module types. We can simply achieve incremental checking and overriding---for example, we want to override "Field a", we simply replace that compiled module with the new module inside the list. This compiled module type serve as an abstraction to let overriding possible.

>>>>

% Concrete details of compilation of a family term data structure
Taking \cref{fig:plugin-example1} as an example: when the user
interactively inputs the line "Field a : nat := ..", our plugin will
translate this statement into the "Module a_9", "Module Type a_10, a_11"
three components. {The "EmptySig" is just empty module type.} Then,
these modules and module types will be generated and type-checked by Coq
immediately. The computed "Module a_10" is then part of the context of
"Field b" (as the module type of "self__A") for "b" to refer to. The
internal representation of family "A" is simply the list of these
``compiled'' modules and module types. We can simply achieve incremental
checking and overriding as in \ref{langdesign-req0}---for example, we
want to override "Field a", we simply replace that compiled module with
the new module inside the list. This compiled module type serve as an
abstraction to let overriding possible.
